Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-07-12 main.tex
placeholder in conclusions
Update on Overleaf.

\author[A. Eemerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

@@

The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
\begin{equation}
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample from
the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$. \textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.

@@

\subsection{Importance of Ionizing Radiation}
\label{sec:ionizing radiation}

We investigate the relative importance of stellar ionizing radiation as a source of feedback in our galaxy with two comparison simulations. We ran one simulation with no stellar ionizing radition (NAME) and a second including only the local effects of stellar ionizing radiation, deleting all photons that travel more than 25~pc from their source star. Although radiative transfer is itself expensive, our simulation without ionizing radiation rapidly formed a significant amount of stars and ended up being more expensive than our fiducial run. We were only able to run this simulation for XXX Myr. We compare the star formation rate

In the first case, we were unable to run the simulation for more than

We compare our fiducial simulation, which includes stellar ionizing radiation traced with radiative transfer, and a simulati

@@

In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters. It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy. This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.

@@

\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work.
%mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
\end{enumerate}

%In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos. This will allow us to examine the role that each source of feedback plays in driving dwarf galaxy chemodynamics.

>>>>

\author[A. Emerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

@@

The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
\begin{equation}
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample from
the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$. \textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution. \textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}

@@

@@

In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters. It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy. This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk. \textbf{The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.} % AE: Mordecai, is this an appropriate clarification of this poitn?

@@

\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work (Emerick et. al. \textit{in prep.}).
\end{enumerate}
